Generate data for multispecies modeling, including diet!

### 2020-10-22 NOBAmsdiets.Rmd
correct fishery age comp dataset, time still ugly fix elsewhere

#add this to om_indices function so that this has years when read in
fish_len_comp_data$time <- as.integer(floor(fish_len_comp_data$time/fstepperyr))

@@

#add this to om_indices function so that this has years when read in
fish_age_comp$time <- fish_age_comp$time/fstepperyr

acompsub <- as.data.frame(age_comp_data$BTS_spring_allbox_effic1[1]) %>% filter(time %in% c(150:270)) %>%
  group_by(species) %>%
  group_map(~ Natageplot(.x), keep = TRUE)

>>>>

#add this to om_indices function so that this has years when read in
#fish_len_comp_data$time <- as.integer(floor(fish_len_comp_data$time/fstepperyr))

@@

#add this to om_indices function so that this has years when read in
#fish_age_comp$time <- fish_age_comp$time/fstepperyr

acompsub <- as.data.frame(fish_age_comp) %>% filter(time %in% c(150:270)) %>%
  group_by(species) %>%
  group_map(~ Natageplot(.x), keep = TRUE)
